---
output: github_document
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qtb

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/qtb)](https://CRAN.R-project.org/package=qtb)
<!-- badges: end -->


**qtb** is a companion tool to the *Joint Market Monitoring Initiative (JMMI)* by REACH. It aims to automate and facilitate the calculation of Minimum Basket Expenditures based on surveys conducted by REACH's field staff using KoBo.

## Name origin

**qtb** pronounced *Q.2.B*  is a reference to a pre-islamic Nabatean  God *al-Kutbay* [^1] or *al-Aktab* [^2] (Arabic: الكتبي)  that was associated with intellect and writing. This god was later assimilated with Hellenistic and Roman gods of commerce.

## Installation

You can install the development version of qtb like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(qtb)
## basic example code
```

## Roadmap

* Weights and Tracked municipalities should be part of user-provided data
* variations calculations and boxplots
* Ability to create a pipeline with {targets} for each data collection period
* Generate tools from a question bank:
  * Option to add cash questions
  * Options to manipulate the municipalities with restrictions on where enumerators collect data

[^1]: https://web.archive.org/web/20060808074330/http://acacialand.com/fawzi.html
[^2]: https://www.britannica.com/topic/Arabian-religion/Pre-Islamic-deities
